### 2012-06-20 docs/makefiles/makefiles.tex
add not about BOXLIB_ONLY

>>>>

\subsection{\boxlib-only Tests}

An even more restrictive setting than {\tt UNIT\_TEST := t} is invoked
by setting {\tt BOXLIB\_ONLY := t}.  This is like the unit test flag,
but does not include {\tt MAESTRO/Source} in the {\tt vpath} search
path for sources.  So this is intended for cases where we don't want
to use any \maestro\ source files.  Typically, this is used in the
small unit tests that live under the various microphysics solvers.  If
a {\tt probin.f90} is built for these tests, it will not include all
the \maestro-specific parameters, but will include any parameters from
the various microphysics routines.
